No proof nets for \capsabbrev{mll} with units

### 2014-05-11 main/LICS.tex
forgot to sync last time - no idea what did ...

\aftersection
%
In this section we will explore the global rewiring behaviour of proof nets.
%
We will look at notions of subnets, and we will give a simple account of equivalence for the fragment of \capsabbrev{mll} that omits the par.
%
Furthermore, we will introduce a notion of relative \emph{parity} between nets, which if odd, guarantees inequivalence.

@@

\begin{proof}
Given a boxing $s$, it follows by induction on the nesting of boxes that the graph over each $s(v)$ satisfies the switching condition.
%
In the other direction, given a sequentialisation of $(\Gamma,\links)$, a box $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
\[
	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
\]
\vskip-12pt
\end{proof}

@@

\begin{proposition}[{\cite[Proposition 2.b]{Bellin-vandeWiele-1995}}]
\label{prop:empire propagation}
The empire $\emp v$ is determined by propagation from $v$: 1) through links; \color{red} 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$; 4) into a par if all its subformulae are in $\emp v-\{v\}$.%;\\ 5) except never into a par or tensor if $v$ is a subformula.
\end{proposition}

Empires are connected to rewiring in the following ways.

\begin{lemma}
\label{lem:rewiring within empire}
For a proof net $(\Gamma,\links)$ where $\links(a)=v$ and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
%
\begin{enumerate}
	\item
$\links\perm*\links'$ where $\links'(a)=w$;
	\item
$w$ is in the empire $\emp a$; and
	\item
in any switching graph for $(\Gamma,\links)$, the path $\path vw$ does not pass through $a$.
\end{enumerate}
\end{lemma}

@@

\color{red}
Rewiring a jump from $\named v\bot$ preserves the empire of $v$, up to that rewiring, by the first lemma below.
%
By the second lemma, the empire of any other vertex $w$ grows or shrinks, or neither, but not both.
\color{black}

@@

	\item
Otherwise, $\Delta=\Delta'$.
\end{enumerate}
\vskip-12pt
\end{proof}

@@

@@

\aftersubsection
A basic observation on \capsabbrev{mll} is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
%
This will hold in general: exchanging the targets of two links generally results in an inequivalent net, in particular when the $\bot$-instances are connected by a tensor.
%
However, a double such exchange commonly does give an equivalent net.

@@

This dynamic will be used to characterise rewiring in the fragment of \capsabbrev{mll} that omits the par.
%
The following standard notion of \emph{balance} characterises provability for it.

@@

\aftersubsection
We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$. We shall find that the parity of equivalent linkings is always even; and that the converse holds when $\Gamma$ is a basic sequent.

@@

\section{Correctness of the encoding}
\label{sec:correctness}

@@

	\item
The link from $i$ is re-attached to $v$ to yield the final configuration.
%
\displayOcto{\octorollA2}%\QEDhere}
\end{enumerate}
\end{proof}

>>>>

\aftersection
%
In this section we will explore the global rewiring behaviour of proof nets.
%
We will look at notions of subnets; we will introduce a notion of relative \emph{parity} between nets, which if odd, guarantees inequivalence; and we will give a simple account of equivalence for the fragment of \capsabbrev{mll} that omits the par.

\color{red}
The notions and results introduced in this section will be used in the main proofs of the paper, in Section~\ref{sec:correctness}, which show that the encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{MLL} proof equivalence, as described informally in the previous section, is correct.
\color{black}

@@

\begin{proof}
Given a boxing $s$, it follows by induction on the nesting of boxes that the graph over each $s(v)$ satisfies the switching condition.
%
In the other direction, given a sequentialisation of $(\Gamma,\links)$, a box $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
\[
	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B} \qedhere
\]
\end{proof}

@@

\begin{proposition}[{\cite[Proposition 2.b]{Bellin-vandeWiele-1995}}]
\label{prop:empire propagation}
The empire $\emp v$ is determined by propagation from $v$: 1) through links; \color{red} 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$; 4) into a par if all its subformulae are in $\emp v-\{v\}$.
\end{proposition}

\noindent
\color{red}
The following three lemmata show how empires are connected to rewiring.
%
Firstly (Lemma~\ref{lem:rewiring within empire}), a jump from $\named v\bot$ may be rewired to exactly those $\1$-occurences that are in the empire of $v$.
%
Secondly (Lemma~\ref{lem:rewiring preserves empire}), rewiring this jump preserves the empire of $v$, up to that rewiring.
%
Thirdly (Lemma~\ref{lem:rewiring affects empires}), the empire of any other vertex $w$ will grow or shrink, or neither, but not both.
\color{black}

\begin{lemma}
\label{lem:rewiring within empire}
For a proof net $(\Gamma,\links)$ where $\links(a)=v$, and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
%
\begin{enumerate}
	\item
$\links\perm*\links'$ where $\links'(a)=w$;
	\item
$w$ is in the empire $\emp a$; and
	\item
in any switching graph for $(\Gamma,\links)$, the path $\path vw$ does not pass through $a$.
\end{enumerate}
\end{lemma}

@@

@@

	\item
Otherwise, $\Delta=\Delta'$. \hfill\qedhere
\end{enumerate}
\end{proof}

@@

\aftersubsection
A basic observation on \capsabbrev{mll} is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
%
This will hold in general: exchanging the targets of two links generally results in an inequivalent net, in particular when the $\bot$-instances are connected by a tensor.

We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$. We shall find that the parity of equivalent linkings is always even; and that the converse holds when $\Gamma$ is a basic sequent.

@@

\aftersubsection

A basic observation on \capsabbrev{mll} is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
%
This will hold in general: exchanging the targets of two links generally results in an inequivalent net, in particular when the $\bot$-instances are connected by a tensor.
%
However, a double such exchange commonly does give an equivalent net.

@@

This dynamic will be used to characterise rewiring in the fragment of \capsabbrev{mll} that omits the par.
%
%The following standard notion of \emph{balance} characterises provability for it.

@@

@@

\section{Formalising the encoding}
\label{sec:correctness}

@@

	\item
The link from $i$ is re-attached to $v$ to yield the final configuration.
%
\displayOcto{\octorollA2}\qedhere
\end{enumerate}
\end{proof}
